\documentclass[english,12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[width=8.50in, height=11.00in, left=0.50in, right=0.50in, top=1in, bottom=1in]{geometry}
\usepackage{babel}
\author{KC1AWV}

\begin{document}
	\begin{center}
		\section*{By-Laws}
	\end{center}
	\section{Secretary}
	It shall be the duty of the Secretary to keep the constitution and By-Laws of the club and have the same with him/her at every meeting. He/she shall note all amendments, changes and additions on the constitution and shall permit it to be consulted by members upon request.
	\section{Membership}
	Full membership is open to licensed Radio Amateurs. \\
	\\
	Associate membership is open to those actively engaged in a class leading to an Amateur Radio license and all other interested persons. \\
	\\
	Full membership includes all club privileges as well as rights to hold a club office and to vote for club officers. \\
	\\
	Associate membership includes all club privileges except for the right to hold office and vote for club officers. \\
	\\
	Applications for membership shall be submitted at regular meetings.
	\section{Meetings}
	Regular meetings shall be held on (day) of each calendar month. Special meetings may be called by the President upon the written request of any five club member. Notices shall be sent to members concerning special meetings and the business to be transacted. Only such business as designated shall be transacted. Such notices shall be sent so that they arrive not less than 24 hours before the meeting.
	\section{Dues, Fees, and Assessments}
	Annual dues of \$xx.00 per member is hereby assessed in accordance with the provisions of Article V of the constitution for the purpose of providing funds for expenses. \\
	\\
	Membership dues are payable in March of each year. \\
	\\
	Any member whose dues are not paid by May 1st will be considered inactive and removed from the membership roster. Inactive members have no voting privileges. \\
	\\
	Termination of membership either by resignation or expulsion will not constitute a refund of dues paid.
	\section{Elections}
	Officer elections will be held annually at the regular November meeting. \\
	\\
	Officers will assume their elected office January 1 of the following year.
	\subsection{Nomination Committee}
	The President will appoint a nomination committee six months prior to elections. \\
	\\
	The committee will be charged with finding qualified candidates to run for office. \\
	\\
	The committee will present a ballot to the president at the regular meeting one month prior to elections at which time the President will entertain a motion for nominations and to accept the ballot. \\
	\\
	The final ballot will be published and made available to all club members by mail. \\
	\\
	The president will dissolve the nomination committee after the annual elections.
	\subsection{Voting}
	Voting will be done using paper ballots. \\
	\\
	Immediately after voting the ballots will be counted openly in front of the membership.\\
	\\
	Any candidate may request a recount of the ballots. \\
	\\
	In the case of an unopposed slate the President may entertain a motion for the Secretary to cast a single ballot. \\
	\section{Interference Committee}
	This committee shall consist of five members (appointed by the club President). The committee shall direct investigation, invite proper inquires, establish technical facts and testimony and report its results to the club.
	\section{Amateur Radio Emergency Service - ARES®}
	ARES® is a program of the American Radio Relay League -- our club will abide by the Rules and Regulations of the ARRL’s Field Organization as they may be amended from time to time, and by ARRL policies, rules, and guidelines contained in ARRL publications.
\end{document}